STAT 405 Project

### 2023-09-23 STAT405Project.qmd
Changed plots

```{r}
plot(length_of_stay, y,  xlab = "Length of Stay", main = "Price vs Length of Stay", ylab = "Price")

@@

```{r}
length_of_stay <- strtoi(cleaned_data$`Length of Stay`)
boxplot(cleaned_data$'Total Costs', 
        main="Box Plot of Total Costs",
        ylab= "Total costs")
```

@@

```{r}
admission_freq <- table(cleaned_data$`Type of Admission`)

barplot(admission_freq, xlab = "Type Of Admission", main = "Frequencies for Type of Admission", ylab = "Frequency")
```
```{r}
medianCosts <- tapply(cleaned_data$`Total Costs`, cleaned_data$Race, median)
barplot(medianCosts, main = "Median Cost by Race", xlab = "Race", ylab = "Median Cost", col = "purple", names.arg = sort(names(medianCosts)), ylim = c(0, max(medianCosts) * 1.5))
```
```{r}
ageGroups <- table(cleaned_data$`Age Group`)
barplot(ageGroups, main = "Age Group Distribution", xlab = "Age Group", 
        ylab = "Frequency", col = "green", border = "black", ylim = c(0, 300000)) 
```

>>>>

```{r}
length_of_stay <- strtoi(cleaned_data$`Length of Stay`)
plot(length_of_stay, y,  xlab = "Length of Stay", main = "Price vs Length of Stay", ylab = "Price")

@@

```{r}

boxplot(cleaned_data$'Total Costs', 
        main="Box Plot of Total Costs",
        ylab= "Total costs")
```

@@

```{r}

# Create the line chart
plot(cleaned_data$`Length of Stay`, cleaned_data$`Total Charges`, type = "l", col = "blue", xlab = "Length of Stay", ylab = "Total Charges", main = "Trends in Total Charges and Length of Stay")

# Add a line for Total Costs
lines(cleaned_data$`Birth Weight`, cleaned_data$`Total Costs`, col = "red")

# Add a legend
legend("topright", legend = c("Total Charges", "Total Costs"), col = c("blue", "red"), lty = 1)

# Add a grid
grid()

#Total cost doesn't change even if length of stay increases and total charge increases.

```
```{r}

heatmap_data <- table(cleaned_data$`Age Group`, cleaned_data$Gender)

row_names <- as.factor(rownames(heatmap_data))
col_names <- as.factor(colnames(heatmap_data))

heatmap(heatmap_data,
        Rowv = NA,          
        Colv = NA,       
        col = colorRampPalette(c("white", "blue"))(50),  
        xlab = "Gender",    
        main = "Gender v. Age Group",  
        labRow = row_names, 
        labCol = col_names)

```
```{r}
ageGroups <- table(cleaned_data$`Age Group`)
barplot(ageGroups, main = "Age Group Distribution", xlab = "Age Group", 
        ylab = "Frequency", col = "green", border = "black", ylim = c(0, 300000)) 
```
